---
title: "Case Study"
output: html_document
---

Loading p8105 data
```{r}
library(p8105.datasets)
library(tidyverse)
library(tibble)
```

```{r}
data(nyc_airbnb)
```

```{r}
nyc_airbnb = 
  nyc_airbnb |> 
  rename(borough = neighbourhood_group) |> 
  mutate(stars = review_scores_location / 2)
```


## Brainstorm questions

- Where are Airbnbs expensive?
  - Borough? Neighborhood?
  - Do other factors (room type) affect price? What about rating?
- How long are Airbnbs active?
  - Are Airbnbs illegal and do they get shut down?
- Which units have the most availability?
- How is review score impacted by locaion
- How many apts are run by one host?


## Do some EDA

Price of Airbnb and the Borough they are located in.

```{r}
nyc_airbnb |> 
  count(borough) 
```

```{r}
nyc_airbnb |> 
  group_by(borough, room_type) |> 
  summarize(median_price = median(price)) |> 
  pivot_wider(
    names_from = room_type, 
    values_from = median_price
  )
```

```{r}
nyc_airbnb |> 
  filter(price < 1000, room_type == "Entire home/apt") |> 
  ggplot(aes(x = price)) +
  geom_histogram() +
  facet_grid(. ~ borough )
```

Use this function to see where the expensive apartment is located
```{r}
nyc_airbnb |> 
  filter(price >= 9500)
```

```{r}
nyc_airbnb |> 
  filter(
    price < 1000, 
    room_type == "Entire home/apt",
    borough == "Manhattan") |> 
  group_by(neighbourhood) |> 
  summarize(
    n_apt = n(),
    mean_price = mean(price)) |> 
  arrange(desc(mean_price))
```

```{r}
nyc_airbnb |> 
  filter(
    price < 1000, 
    room_type == "Entire home/apt",
    borough == "Manhattan") |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price))
```

## Try to make a map

```{r}
nyc_airbnb |> 
  filter(
    price < 1000, 
    room_type == "Entire home/apt",
    borough == "Manhattan") |> 
  ggplot(aes(x = lat, y = long, color = price)) + 
  geom_point()
```

Try something else entirely. 

```{r}
library(leaflet)
```


```{r}
nyc_airbnb |>  
  filter(
    price < 1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") |>
  sample_n(500) |> 
  leaflet() |> 
  addProviderTiles(providers$CartoDB.Positron) |> 
  addCircleMarkers(~lat, ~long, radius = .5)
```

